---
title: "Randomization and non-concurrent controls"
author: ""
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: true
    number_sections: true
    code_folding: hide 
    theme: readable
    # journal, readable, paper 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      cache = TRUE)
```

```{r, include = FALSE}
library(tidyverse)

source("../functions/linear_model.R") #script model-based approaches  
source("../functions/log_model.R") #script model-based approaches  
source("../functions/trend_functions.R") #script time trends
source("../functions/data_sim.R") #script data generation randomization procedure I
source("../functions/data_sim_rdt.R") #script data generation randomization procedure II
source("../functions/data_sim_block.R") #script data generation randomization procedure III
source("../functions/data_sim_brdt.R") #script data generation randomization procedure VI
```

```{r}
set.seed(3214)
```


# Continuous endpoints

```{r}
alpha=0.025
delta=c(0.25,0)
OR=c(1.8,1)

nsim=100000
```

## Simple randomization per period

### Deterministic times 

#### Extreme time trend

```{r}
# Extreme time trend

x <- replicate(nsim,
               linear_model_a2(data=data_sim(K=1, mu0=0, delta=c(0.25,0), lambda=c(5,5,5), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", endpoint="continuous"),
                               delta=delta, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

#### Moderate time trend

```{r}
# Moderate time trend
x <- replicate(nsim,
               linear_model_a2(data=data_sim(K=1, mu0=0, delta=c(0.25,0), lambda=c(.15,.15,.15), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", endpoint="continuous"),
                               delta=delta, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```


### Random times

#### Extreme time trend

```{r}
# Extreme time trend
x <- replicate(nsim,
               linear_model_a2(data=data_sim_rdt(K=1, mu0=0, delta=c(0.25,0), lambda=c(5,5,5), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", endpoint="continuous"),
                               delta=delta, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

#### Moderate time trend

```{r}
# Moderate time trend
x <- replicate(nsim,
               linear_model_a2(data=data_sim_rdt(K=1, mu0=0, delta=c(0.25,0), lambda=c(.15,.15,.15), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", endpoint="continuous"),
                               delta=delta, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```


## Block randomization

### Deterministic times 

#### Extreme time trend

```{r}
# Extreme time trend
x <- replicate(nsim,
               linear_model_a2(data=data_sim_block(K=1, mu0=0, delta=c(0.25,0), lambda=c(5,5,5), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", endpoint="continuous"),
                               delta=delta, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

#### Moderate time trend

```{r}
# Moderate time trend
x <- replicate(nsim,
               linear_model_a2(data=data_sim_block(K=1, mu0=0, delta=c(0.25,0), lambda=c(.15,.15,.15), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", endpoint="continuous"),
                               delta=delta, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

### Random times

#### Extreme time trend

```{r}
# Extreme time trend
x <- replicate(nsim,
               linear_model_a2(data=data_sim_brdt(K=1, mu0=0, delta=c(0.25,0), lambda=c(5,5,5), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", endpoint="continuous"),
                               delta=delta, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

#### Moderate time trend

```{r}
# Moderate time trend
x <- replicate(nsim,
               linear_model_a2(data=data_sim_brdt(K=1, mu0=0, delta=c(0.25,0), lambda=c(.15,.15,.15), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", endpoint="continuous"),
                               delta=delta, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```


# Binary endpoints

## Simple randomization per period

### Deterministic times 

#### Extreme time trend

```{r}
# Extreme time trend
x <- replicate(nsim,
               logistic_model_a2(data=data_sim(K=1, p0 = 0.3, OR=c(1.8,1), lambda=c(5,5,5), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", trend_param = "mult", endpoint="binary"),
                               OR=OR, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

#### Moderate time trend

```{r}
# Moderate time trend
x <- replicate(nsim,
               logistic_model_a2(data=data_sim(K=1, p0 = 0.3, OR=c(1.8,1), lambda=c(.15,.15,.15), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", trend_param = "mult", endpoint="binary"),
                               OR=OR, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

### Random times

#### Extreme time trend

```{r}
# Extreme time trend
x <- replicate(nsim,
               logistic_model_a2(data=data_sim_rdt(K=1, p0 = 0.3, OR=c(1.8,1), lambda=c(5,5,5), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", trend_param = "mult", endpoint="binary"),
                               OR=OR, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

#### Moderate time trend

```{r}
# Moderate time trend
x <- replicate(nsim,
               logistic_model_a2(data=data_sim_rdt(K=1, p0 = 0.3, OR=c(1.8,1), lambda=c(.15,.15,.15), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", trend_param = "mult", endpoint="binary"),
                               OR=OR, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

## Block randomization

### Deterministic times

#### Extreme time trend

```{r}
# Extreme time trend
x <- replicate(nsim,
               logistic_model_a2(data=data_sim_block(K=1, p0 = 0.3, OR=c(1.8,1), lambda=c(5,5,5), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", trend_param = "mult", endpoint="binary"),
                               OR=OR, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

#### Moderate time trend

```{r}
# Moderate time trend
x <- replicate(nsim,
               logistic_model_a2(data=data_sim_block(K=1, p0 = 0.3, OR=c(1.8,1), lambda=c(.15,.15,.15), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", trend_param = "mult", endpoint="binary"),
                               OR=OR, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

### Random times

#### Extreme time trend

```{r}
# Extreme time trend
x <- replicate(nsim,
               logistic_model_a2(data=data_sim_brdt(K=1, p0 = 0.3, OR=c(1.8,1), lambda=c(5,5,5), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", trend_param = "mult", endpoint="binary"),
                               OR=OR, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```

#### Moderate time trend

```{r}
# Moderate time trend
x <- replicate(nsim,
               logistic_model_a2(data=data_sim_brdt(K=1, p0 = 0.3, OR=c(1.8,1), lambda=c(.15,.15,.15), sigma=1, N1=c(125,125), N2=c(125,125), N_add=250, trend="linear2", trend_param = "mult", endpoint="binary"),
                               OR=OR, alpha=alpha)[3])
sum(as.numeric(x))/nsim
```


































