---
title: "CORRECTION: Model-based time trend adjustments in platform trials with NCC"
author: ''
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: yes
    code_folding: hide
    theme: readable
  pdf_document:
    toc: yes
    toc_depth: 3
---

```{r setup, include = FALSE}
library(tidyverse)
library(latex2exp)
library(ggpubr)
library(ggnewscale)
library(RColorBrewer)
library(ggsci)
library(scales)

# source("functions/linear_model.R")
# source("functions/log_model.R")
# source("functions/z_test.R")
# source("functions/t_test.R")
# source("functions/z_prop_test.R")
# source("functions/trend_functions.R")
# source("functions/data_sim_block.R")
# source("functions/allinone_model.R")
# source("functions/allinone_sim.R")
# source("functions/allinone_sim_par.R")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message = FALSE,
  warning = FALSE)
```


# Preamble


We have recently noticed that an R coding issue resulted in numerical errors in the reported results for the bias. Specifically, the results presented in Figures S8, S9, S14 and S15 are not correct. In the case of linear and inverted-U time trends, correction of coding errors in the bias computation produced such small changes to data presented in the previously mentioned Figures as to be indistinguishable from the corrected version. However, in the case of stepwise time trends, it is now clearer that the results of the separate analysis reported no bias. The updated Figures come next. For details regarding the definition of time trend patterns, see \href{https://pavlakrotka.github.io/NCC/reference/}{https://pavlakrotka.github.io/NCC/}.




```{r}
# Load data - NEW

# Binary stepwise
results_bin_step_add_alpha_eq_new <- read_csv("results/results_bin_step_add_alpha_eq.csv")
results_bin_step_mult_alpha_eq_new <- read_csv("results/results_bin_step_mult_alpha_eq.csv")
results_bin_step_add_pow_eq_new <- read_csv("results/results_bin_step_add_pow_eq.csv")
results_bin_step_mult_pow_eq_new <- read_csv("results/results_bin_step_mult_pow_eq.csv")

results_bin_step_add_alpha_OR1_eq_new <- read_csv("results/results_bin_step_add_alpha_OR1_eq.csv")
results_bin_step_mult_alpha_OR1_eq_new <- read_csv("results/results_bin_step_mult_alpha_OR1_eq.csv")
results_bin_step_add_pow_OR1_eq_new <- read_csv("results/results_bin_step_add_pow_OR1_eq.csv")
results_bin_step_mult_pow_OR1_eq_new <- read_csv("results/results_bin_step_mult_pow_OR1_eq.csv")

results_bin_step_mult_alpha_diff_neg_new <- read_csv("results/results_bin_step_mult_alpha_diff_neg.csv")
results_bin_step_mult_pow_diff_neg_new <- read_csv("results/results_bin_step_mult_pow_diff_neg.csv")
results_bin_step_mult_alpha_OR1_diff_neg_new <- read_csv("results/results_bin_step_mult_alpha_OR1_diff_neg.csv")
results_bin_step_mult_pow_OR1_diff_neg_new <- read_csv("results/results_bin_step_mult_pow_OR1_diff_neg.csv")

results_bin_step_mult_alpha_diff_pos_new <- read_csv("results/results_bin_step_mult_alpha_diff_pos.csv")
results_bin_step_mult_pow_diff_pos_new <- read_csv("results/results_bin_step_mult_pow_diff_pos.csv")
results_bin_step_mult_alpha_OR1_diff_pos_new <- read_csv("results/results_bin_step_mult_alpha_OR1_diff_pos.csv")
results_bin_step_mult_pow_OR1_diff_pos_new <- read_csv("results/results_bin_step_mult_pow_OR1_diff_pos.csv")

# Binary linear

results_bin_lin_add_alpha_eq_new <- read_csv("results/results_bin_lin_add_alpha_eq.csv")
results_bin_lin_mult_alpha_eq_new <- read_csv("results/results_bin_lin_mult_alpha_eq.csv")
results_bin_lin_add_pow_eq_new <- read_csv("results/results_bin_lin_add_pow_eq.csv")
results_bin_lin_mult_pow_eq_new <- read_csv("results/results_bin_lin_mult_pow_eq.csv")

results_bin_lin_add_alpha_OR1_eq_new <- read_csv("results/results_bin_lin_add_alpha_OR1_eq.csv")
results_bin_lin_mult_alpha_OR1_eq_new <- read_csv("results/results_bin_lin_mult_alpha_OR1_eq.csv")
results_bin_lin_add_pow_OR1_eq_new <- read_csv("results/results_bin_lin_add_pow_OR1_eq.csv")
results_bin_lin_mult_pow_OR1_eq_new <- read_csv("results/results_bin_lin_mult_pow_OR1_eq.csv")

results_bin_lin_mult_alpha_diff_neg_new <- read_csv("results/results_bin_lin_mult_alpha_diff_neg.csv")
results_bin_lin_mult_pow_diff_neg_new <- read_csv("results/results_bin_lin_mult_pow_diff_neg.csv")
results_bin_lin_mult_alpha_OR1_diff_neg_new <- read_csv("results/results_bin_lin_mult_alpha_OR1_diff_neg.csv")
results_bin_lin_mult_pow_OR1_diff_neg_new <- read_csv("results/results_bin_lin_mult_pow_OR1_diff_neg.csv")

results_bin_lin_mult_alpha_diff_pos_new <- read_csv("results/results_bin_lin_mult_alpha_diff_pos.csv")
results_bin_lin_mult_pow_diff_pos_new <- read_csv("results/results_bin_lin_mult_pow_diff_pos.csv")
results_bin_lin_mult_alpha_OR1_diff_pos_new <- read_csv("results/results_bin_lin_mult_alpha_OR1_diff_pos.csv")
results_bin_lin_mult_pow_OR1_diff_pos_new <- read_csv("results/results_bin_lin_mult_pow_OR1_diff_pos.csv")

# Binary inverted U-1

results_bin_inv_1_add_alpha_eq_new <- read_csv("results/results_bin_inv_1_add_alpha_eq.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_alpha_eq_new <- read_csv("results/results_bin_inv_1_mult_alpha_eq.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_add_pow_eq_new <- read_csv("results/results_bin_inv_1_add_pow_eq.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_pow_eq_new <- read_csv("results/results_bin_inv_1_mult_pow_eq.csv") %>%
  mutate(trend = "inv_u_1")

results_bin_inv_1_add_alpha_OR1_eq_new <- read_csv("results/results_bin_inv_1_add_alpha_OR1_eq.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_alpha_OR1_eq_new <- read_csv("results/results_bin_inv_1_mult_alpha_OR1_eq.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_add_pow_OR1_eq_new <- read_csv("results/results_bin_inv_1_add_pow_OR1_eq.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_pow_OR1_eq_new <- read_csv("results/results_bin_inv_1_mult_pow_OR1_eq.csv") %>%
  mutate(trend = "inv_u_1")

results_bin_inv_1_mult_alpha_diff_neg_new <- read_csv("results/results_bin_inv_1_mult_alpha_diff_neg.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_pow_diff_neg_new <- read_csv("results/results_bin_inv_1_mult_pow_diff_neg.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_alpha_OR1_diff_neg_new <- read_csv("results/results_bin_inv_1_mult_alpha_OR1_diff_neg.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_pow_OR1_diff_neg_new <- read_csv("results/results_bin_inv_1_mult_pow_OR1_diff_neg.csv") %>%
  mutate(trend = "inv_u_1")

results_bin_inv_1_mult_alpha_diff_pos_new <- read_csv("results/results_bin_inv_1_mult_alpha_diff_pos.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_pow_diff_pos_new <- read_csv("results/results_bin_inv_1_mult_pow_diff_pos.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_alpha_OR1_diff_pos_new <- read_csv("results/results_bin_inv_1_mult_alpha_OR1_diff_pos.csv") %>%
  mutate(trend = "inv_u_1")
results_bin_inv_1_mult_pow_OR1_diff_pos_new <- read_csv("results/results_bin_inv_1_mult_pow_OR1_diff_pos.csv") %>%
  mutate(trend = "inv_u_1")

# Binary inverted U-2

results_bin_inv_2_add_alpha_eq_new <- read_csv("results/results_bin_inv_2_add_alpha_eq.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_alpha_eq_new <- read_csv("results/results_bin_inv_2_mult_alpha_eq.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_add_pow_eq_new <- read_csv("results/results_bin_inv_2_add_pow_eq.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_pow_eq_new <- read_csv("results/results_bin_inv_2_mult_pow_eq.csv") %>%
  mutate(trend = "inv_u_2")

results_bin_inv_2_add_alpha_OR1_eq_new <- read_csv("results/results_bin_inv_2_add_alpha_OR1_eq.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_alpha_OR1_eq_new <- read_csv("results/results_bin_inv_2_mult_alpha_OR1_eq.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_add_pow_OR1_eq_new <- read_csv("results/results_bin_inv_2_add_pow_OR1_eq.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_pow_OR1_eq_new <- read_csv("results/results_bin_inv_2_mult_pow_OR1_eq.csv") %>%
  mutate(trend = "inv_u_2")

results_bin_inv_2_mult_alpha_diff_neg_new <- read_csv("results/results_bin_inv_2_mult_alpha_diff_neg.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_pow_diff_neg_new <- read_csv("results/results_bin_inv_2_mult_pow_diff_neg.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_alpha_OR1_diff_neg_new <- read_csv("results/results_bin_inv_2_mult_alpha_OR1_diff_neg.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_pow_OR1_diff_neg_new <- read_csv("results/results_bin_inv_2_mult_pow_OR1_diff_neg.csv") %>%
  mutate(trend = "inv_u_2")

results_bin_inv_2_mult_alpha_diff_pos_new <- read_csv("results/results_bin_inv_2_mult_alpha_diff_pos.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_pow_diff_pos_new <- read_csv("results/results_bin_inv_2_mult_pow_diff_pos.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_alpha_OR1_diff_pos_new <- read_csv("results/results_bin_inv_2_mult_alpha_OR1_diff_pos.csv") %>%
  mutate(trend = "inv_u_2")
results_bin_inv_2_mult_pow_OR1_diff_pos_new <- read_csv("results/results_bin_inv_2_mult_pow_OR1_diff_pos.csv") %>%
  mutate(trend = "inv_u_2")

# Binary inverted U-3

results_bin_inv_3_add_alpha_eq_new <- read_csv("results/results_bin_inv_3_add_alpha_eq.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_alpha_eq_new <- read_csv("results/results_bin_inv_3_mult_alpha_eq.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_add_pow_eq_new <- read_csv("results/results_bin_inv_3_add_pow_eq.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_pow_eq_new <- read_csv("results/results_bin_inv_3_mult_pow_eq.csv") %>%
  mutate(trend = "inv_u_3")

results_bin_inv_3_add_alpha_OR1_eq_new <- read_csv("results/results_bin_inv_3_add_alpha_OR1_eq.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_alpha_OR1_eq_new <- read_csv("results/results_bin_inv_3_mult_alpha_OR1_eq.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_add_pow_OR1_eq_new <- read_csv("results/results_bin_inv_3_add_pow_OR1_eq.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_pow_OR1_eq_new <- read_csv("results/results_bin_inv_3_mult_pow_OR1_eq.csv") %>%
  mutate(trend = "inv_u_3")

results_bin_inv_3_mult_alpha_diff_neg_new <- read_csv("results/results_bin_inv_3_mult_alpha_diff_neg.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_pow_diff_neg_new <- read_csv("results/results_bin_inv_3_mult_pow_diff_neg.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_alpha_OR1_diff_neg_new <- read_csv("results/results_bin_inv_3_mult_alpha_OR1_diff_neg.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_pow_OR1_diff_neg_new <- read_csv("results/results_bin_inv_3_mult_pow_OR1_diff_neg.csv") %>%
  mutate(trend = "inv_u_3")

results_bin_inv_3_mult_alpha_diff_pos_new <- read_csv("results/results_bin_inv_3_mult_alpha_diff_pos.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_pow_diff_pos_new <- read_csv("results/results_bin_inv_3_mult_pow_diff_pos.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_alpha_OR1_diff_pos_new <- read_csv("results/results_bin_inv_3_mult_alpha_OR1_diff_pos.csv") %>%
  mutate(trend = "inv_u_3")
results_bin_inv_3_mult_pow_OR1_diff_pos_new <- read_csv("results/results_bin_inv_3_mult_pow_OR1_diff_pos.csv") %>%
  mutate(trend = "inv_u_3")
```

```{r}
my_palette = c("#ED0000FF",
               "#925E9FFF",
               "#00468BFF",
               "#42B540FF",
               "#EEAD0E",
               "#0099B4FF",
               "#FDAF91FF",
               "#ADB6B6FF",
               "#1B1919FF")

#show_col(my_palette)
```


```{r}
# Functions

get_data_plot <- function(data_csv){
  
  data_reject <- data_csv %>%
    select(c(1:21, starts_with("reject"), scenario, alpha)) %>%
    pivot_longer(cols = starts_with("reject"),
                 names_to = c("model"),
                 names_prefix = "reject_h02_",
                 values_to = "reject_h02")
  
  data_rMSE <- data_csv %>%
    select(c(1:21, starts_with("rMSE"), scenario, alpha)) %>%
    pivot_longer(cols = starts_with("rMSE"),
                 names_to = c("model"),
                 names_prefix = "rMSE_",
                 values_to = "rMSE")
  
  data_bias <- data_csv %>%
    select(c(1:21, starts_with("bias"), scenario, alpha)) %>%
    pivot_longer(cols = starts_with("bias"),
                 names_to = c("model"),
                 names_prefix = "bias_",
                 values_to = "bias")
  
  data_plot <- data_reject %>%
    left_join(data_rMSE) %>%
    left_join(data_bias)
  
  data_plot
}


get_data_plot_prob <- function(data_csv){
  
  data_reject <- data_csv %>%
    select(c(1:21, starts_with("reject"), scenario, p_0, p_1, p_2, alpha)) %>%
    pivot_longer(cols = starts_with("reject"),
                 names_to = c("model"),
                 names_prefix = "reject_h02_",
                 values_to = "reject_h02")
  
  data_rMSE <- data_csv %>%
    select(c(1:21, starts_with("rMSE"), scenario, p_0, p_1, p_2, alpha)) %>%
    pivot_longer(cols = starts_with("rMSE"),
                 names_to = c("model"),
                 names_prefix = "rMSE_",
                 values_to = "rMSE")
  
  data_bias <- data_csv %>%
    select(c(1:21, starts_with("bias"), scenario, p_0, p_1, p_2, alpha)) %>%
    pivot_longer(cols = starts_with("bias"),
                 names_to = c("model"),
                 names_prefix = "bias_",
                 values_to = "bias")
  
  data_p_a2 <- data_csv %>%
    select(c(1:21, starts_with("p_a2"), scenario, p_0, p_1, p_2, alpha)) %>%
    pivot_longer(cols = starts_with("p_a2"),
                 names_to = c("OR_RR_RD"),
                 names_prefix = "p_a2_",
                 values_to = "p_a2")
  
  data_plot <- data_reject %>%
    left_join(data_rMSE) %>%
    left_join(data_bias) %>%
    left_join(data_p_a2)
  
  data_plot
}


get_data_plot_prob_1 <- function(data_csv){
  
  data_reject <- data_csv %>%
    select(c(1:21, starts_with("reject"), scenario, p_0, p_1, p_2, alpha, hypothesis_1, OR_1)) %>%
    pivot_longer(cols = starts_with("reject"),
                 names_to = c("model"),
                 names_prefix = "reject_h02_",
                 values_to = "reject_h02")
  
  data_rMSE <- data_csv %>%
    select(c(1:21, starts_with("rMSE"), scenario, p_0, p_1, p_2, alpha, hypothesis_1, OR_1)) %>%
    pivot_longer(cols = starts_with("rMSE"),
                 names_to = c("model"),
                 names_prefix = "rMSE_",
                 values_to = "rMSE")
  
  data_bias <- data_csv %>%
    select(c(1:21, starts_with("bias"), scenario, p_0, p_1, p_2, alpha, hypothesis_1, OR_1)) %>%
    pivot_longer(cols = starts_with("bias"),
                 names_to = c("model"),
                 names_prefix = "bias_",
                 values_to = "bias")
  
  data_p_a2 <- data_csv %>%
    select(c(1:21, starts_with("p_a2"), scenario, p_0, p_1, p_2, alpha, hypothesis_1, OR_1)) %>%
    pivot_longer(cols = starts_with("p_a2"),
                 names_to = c("OR_RR_RD"),
                 names_prefix = "p_a2_",
                 values_to = "p_a2")
  
  data_plot <- data_reject %>%
    left_join(data_rMSE) %>%
    left_join(data_bias) %>%
    left_join(data_p_a2)
  
  data_plot
}


get_data_plot_mu <- function(data_csv){
  
  data_reject <- data_csv %>%
    select(c(1:20, starts_with("reject"), scenario, mu_0, mu_1, mu_2, alpha)) %>%
    pivot_longer(cols = starts_with("reject"),
                 names_to = c("model"),
                 names_prefix = "reject_h02_",
                 values_to = "reject_h02")
  
  data_rMSE <- data_csv %>%
    select(c(1:20, starts_with("rMSE"), scenario, mu_0, mu_1, mu_2, alpha)) %>%
    pivot_longer(cols = starts_with("rMSE"),
                 names_to = c("model"),
                 names_prefix = "rMSE_",
                 values_to = "rMSE")
  
  data_bias <- data_csv %>%
    select(c(1:20, starts_with("bias"), scenario, mu_0, mu_1, mu_2, alpha)) %>%
    pivot_longer(cols = starts_with("bias"),
                 names_to = c("model"),
                 names_prefix = "bias_",
                 values_to = "bias")
  
  data_plot <- data_reject %>%
    left_join(data_rMSE) %>%
    left_join(data_bias)
  
  data_plot
}


get_OR_RR_RD <- function(p_c1, p_c2, p_a1){
  OR_c <- (p_c1/(1-p_c1))/(p_c2/(1-p_c2))
  O_a1 <- (p_a1/(1-p_a1))
  p_a2_OR <- (O_a1/OR_c)/(1+(O_a1/OR_c))
  
  p_a2_RR <- p_a1/(p_c1/p_c2)
  
  p_a2_RD <- p_a1-p_c1+p_c2
  
  return(list(p_a2_OR=p_a2_OR, p_a2_RR=p_a2_RR, p_a2_RD=p_a2_RD))
}
```


# Binary endpoint - equal trends

```{r}
results_bin_eq_step_new <- rbind(results_bin_step_mult_alpha_eq_new,
                                 results_bin_step_mult_pow_eq_new,
                                 results_bin_step_mult_alpha_OR1_eq_new,
                                 results_bin_step_mult_pow_OR1_eq_new)

results_bin_eq_lin_new <- rbind(results_bin_lin_mult_alpha_eq_new,
                                results_bin_lin_mult_pow_eq_new,
                                results_bin_lin_mult_alpha_OR1_eq_new,
                                results_bin_lin_mult_pow_OR1_eq_new)

results_bin_eq_inv_1_new <- rbind(results_bin_inv_1_mult_alpha_eq_new,
                                  results_bin_inv_1_mult_pow_eq_new,
                                  results_bin_inv_1_mult_alpha_OR1_eq_new,
                                  results_bin_inv_1_mult_pow_OR1_eq_new)

results_bin_eq_inv_2_new <- rbind(results_bin_inv_2_mult_alpha_eq_new,
                                  results_bin_inv_2_mult_pow_eq_new,
                                  results_bin_inv_2_mult_alpha_OR1_eq_new,
                                  results_bin_inv_2_mult_pow_OR1_eq_new)

results_bin_eq_inv_3_new <- rbind(results_bin_inv_3_mult_alpha_eq_new,
                                  results_bin_inv_3_mult_pow_eq_new,
                                  results_bin_inv_3_mult_alpha_OR1_eq_new,
                                  results_bin_inv_3_mult_pow_OR1_eq_new)

results_bin_eq_new <- rbind(results_bin_eq_step_new,
                            results_bin_eq_lin_new,
                            results_bin_eq_inv_1_new %>% select(-N_peak),
                            results_bin_eq_inv_2_new %>% select(-N_peak),
                            results_bin_eq_inv_3_new %>% select(-N_peak)) %>%
  mutate(scenario = factor(case_when(trend_param=="add" & lambda0 >=0 ~ "add_pos",
                                     trend_param=="add" & lambda0 <0 ~ "add_neg",
                                     trend_param=="mult" & lambda0 >=0 ~ "mult_pos",
                                     trend_param=="mult" & lambda0 <0 ~ "mult_neg"),
                           levels = c("add_neg", "add_pos", "mult_neg", "mult_pos")),
         alpha = ifelse(hypothesis %in% c("H0", "H0_1"), 0.025, NA))
```

## Bias (Fig. S8) - corrected


```{r, fig.width=10, fig.height=10}
hypothesis_names <- c(H0="Null hypothesis (OR1<1)", H1="Alter. hypothesis (OR1<1)", H0_1="Null hypothesis (OR1>1)", H1_1="Alter. hypothesis (OR1>1)")
trend_names <- c(linear = "Linear", stepwise = "Stepwise", inv_u_1 = "Inverted-U (N[p] == 125)", inv_u_2 = "Inverted-U (N[p] == 250)", inv_u_3 = "Inverted-U (N[p] == 500)")

ggplot(get_data_plot(results_bin_eq_new) %>% filter(model!="zsep" & model!="zpol")) +
  #geom_point(aes(lambda1, bias, color=as.factor(model))) +
  geom_line(aes(lambda1, bias, color=as.factor(model)), size=1) +
  facet_grid(hypothesis ~ trend, scales = "free", 
             labeller = labeller(hypothesis  = as_labeller(hypothesis_names),
                                 trend = as_labeller(trend_names, label_parsed))) +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom") +
  labs(x=TeX("$\\lambda$"), color="Analysis approach:", y="Bias") +
  scale_color_manual(values = my_palette, labels = c("ALLTC-Linear", "ALLTCI-Linear", "ALLTC-Step", "ALLTCI-Step", "TC-Linear", "TC-Step", "Pooled approach", "Separate approach")) +
  scale_x_continuous(n.breaks = 3)

ggsave("figures/bin_all_eq_bias_supp_new.png", width = 10, height = 10)
```

## rMSE (Fig. S9) - corrected

```{r, fig.width=10, fig.height=10}
hypothesis_names <- c(H0="Null hypothesis (OR1<1)", H1="Alter. hypothesis (OR1<1)", H0_1="Null hypothesis (OR1>1)", H1_1="Alter. hypothesis (OR1>1)")
trend_names <- c(linear = "Linear", stepwise = "Stepwise", inv_u_1 = "Inverted-U (N[p] == 125)", inv_u_2 = "Inverted-U (N[p] == 250)", inv_u_3 = "Inverted-U (N[p] == 500)")

ggplot(get_data_plot(results_bin_eq_new) %>% filter(model!="zsep" & model!="zpol")) +
  #geom_point(aes(lambda1, rMSE, color=as.factor(model))) +
  geom_line(aes(lambda1, rMSE, color=as.factor(model)), size=1) +
  facet_grid(hypothesis ~ trend, scales = "free", 
             labeller = labeller(hypothesis  = as_labeller(hypothesis_names),
                                 trend = as_labeller(trend_names, label_parsed))) +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom") +
  labs(x=TeX("$\\lambda$"), color="Analysis approach:", y="rMSE") +
  scale_color_manual(values = my_palette, labels = c("ALLTC-Linear", "ALLTCI-Linear", "ALLTC-Step", "ALLTCI-Step", "TC-Linear", "TC-Step", "Pooled approach", "Separate approach")) +
  scale_x_continuous(n.breaks = 3)

ggsave("figures/bin_all_eq_rmse_supp_new.png", width = 10, height = 10)
```


# Binary endpoints - different trends

```{r}
results_bin_diff_step_new <- rbind(results_bin_step_mult_alpha_diff_neg_new,
                                   results_bin_step_mult_pow_diff_neg_new,
                                   results_bin_step_mult_alpha_OR1_diff_neg_new,
                                   results_bin_step_mult_pow_OR1_diff_neg_new,
                                   results_bin_step_mult_alpha_diff_pos_new,
                                   results_bin_step_mult_pow_diff_pos_new,
                                   results_bin_step_mult_alpha_OR1_diff_pos_new,
                                   results_bin_step_mult_pow_OR1_diff_pos_new) %>%
  mutate(scenario = factor(case_when(trend_param=="add" & lambda0 >=0 ~ "add_pos",
                                     trend_param=="add" & lambda0 <0 ~ "add_neg",
                                     trend_param=="mult" & lambda0 >=0 ~ "mult_pos",
                                     trend_param=="mult" & lambda0 <0 ~ "mult_neg"),
                           levels = c("add_neg", "add_pos", "mult_neg", "mult_pos"))) %>%
  
  mutate(p_0 = case_when(trend_param=="mult" & trend=="stepwise" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + lambda0))),
                         trend_param=="mult" & trend=="linear" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + lambda0*((n0+n1+n22)-1)/((n0+n1+n22)-1))))), # P_control 2nd period
         
         p_1 = case_when(trend_param=="mult" & trend=="stepwise" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR1) + lambda1))),
                         trend_param=="mult" & trend=="linear" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR1) + lambda1*((n0+n1+n22)-1)/((n0+n1+n22)-1))))), # P_t1 2nd period
         
         p_2 = case_when(trend_param=="mult" & trend=="stepwise" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR2) + lambda2))),
                         trend_param=="mult" & trend=="linear" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR2) + lambda2*((n0+n1+n22)-1)/((n0+n1+n22)-1))))), # P_t2 2nd period
         
         p1 = case_when(trend_param=="mult" & trend=="stepwise" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR1)))),
                        trend_param=="mult" & trend=="linear" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR1) + lambda1*(1)/((n0+n1+n22)-1)))))) # P_t1 1st period


results_bin_diff_step_new <- results_bin_diff_step_new %>%
  mutate(p_a2_OR = get_OR_RR_RD(p_c1 = results_bin_diff_step_new$p0, p_c2 = results_bin_diff_step_new$p_0, p_a1 = results_bin_diff_step_new$p1)$p_a2_OR,
         p_a2_RR = get_OR_RR_RD(p_c1 = results_bin_diff_step_new$p0, p_c2 = results_bin_diff_step_new$p_0, p_a1 = results_bin_diff_step_new$p1)$p_a2_RR,
         p_a2_RD = get_OR_RR_RD(p_c1 = results_bin_diff_step_new$p0, p_c2 = results_bin_diff_step_new$p_0, p_a1 = results_bin_diff_step_new$p1)$p_a2_RD,
         alpha = ifelse(hypothesis %in% c("H0", "H0_1"), 0.025, NA))

results_bin_diff_lin_new <- rbind(results_bin_lin_mult_alpha_diff_neg_new,
                                  results_bin_lin_mult_pow_diff_neg_new,
                                  results_bin_lin_mult_alpha_OR1_diff_neg_new,
                                  results_bin_lin_mult_pow_OR1_diff_neg_new,
                                  results_bin_lin_mult_alpha_diff_pos_new,
                                  results_bin_lin_mult_pow_diff_pos_new,
                                  results_bin_lin_mult_alpha_OR1_diff_pos_new,
                                  results_bin_lin_mult_pow_OR1_diff_pos_new) %>%
  mutate(scenario = factor(case_when(trend_param=="add" & lambda0 >=0 ~ "add_pos",
                                     trend_param=="add" & lambda0 <0 ~ "add_neg",
                                     trend_param=="mult" & lambda0 >=0 ~ "mult_pos",
                                     trend_param=="mult" & lambda0 <0 ~ "mult_neg"),
                           levels = c("add_neg", "add_pos", "mult_neg", "mult_pos")))  %>%
  
  mutate(p_0 = case_when(trend_param=="mult" & trend=="stepwise" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + lambda0))),
                         trend_param=="mult" & trend=="linear" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + lambda0*((n0+n1+n22)-1)/((n0+n1+n22)-1))))), # P_control 2nd period
         
         p_1 = case_when(trend_param=="mult" & trend=="stepwise" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR1) + lambda1))),
                         trend_param=="mult" & trend=="linear" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR1) + lambda1*((n0+n1+n22)-1)/((n0+n1+n22)-1))))), # P_t1 2nd period
         
         p_2 = case_when(trend_param=="mult" & trend=="stepwise" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR2) + lambda2))),
                         trend_param=="mult" & trend=="linear" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR2) + lambda2*((n0+n1+n22)-1)/((n0+n1+n22)-1))))), # P_t2 2nd period
         
         p1 = case_when(trend_param=="mult" & trend=="stepwise" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR1)))),
                        trend_param=="mult" & trend=="linear" ~ 1 / (1 + exp(-(log(p0/(1-p0)) + log(OR1) + lambda1*(1)/((n0+n1+n22)-1)))))) # P_t1 1st period


results_bin_diff_lin_new <- results_bin_diff_lin_new %>%
  mutate(p_a2_OR = get_OR_RR_RD(p_c1 = results_bin_diff_lin_new$p0, p_c2 = results_bin_diff_lin_new$p_0, p_a1 = results_bin_diff_lin_new$p1)$p_a2_OR,
         p_a2_RR = get_OR_RR_RD(p_c1 = results_bin_diff_lin_new$p0, p_c2 = results_bin_diff_lin_new$p_0, p_a1 = results_bin_diff_lin_new$p1)$p_a2_RR,
         p_a2_RD = get_OR_RR_RD(p_c1 = results_bin_diff_lin_new$p0, p_c2 = results_bin_diff_lin_new$p_0, p_a1 = results_bin_diff_lin_new$p1)$p_a2_RD,
         alpha = ifelse(hypothesis %in% c("H0", "H0_1"), 0.025, NA))

results_bin_diff_inv_1_new <- rbind(results_bin_inv_1_mult_alpha_diff_neg_new,
                                    results_bin_inv_1_mult_pow_diff_neg_new,
                                    results_bin_inv_1_mult_alpha_OR1_diff_neg_new,
                                    results_bin_inv_1_mult_pow_OR1_diff_neg_new,
                                    results_bin_inv_1_mult_alpha_diff_pos_new,
                                    results_bin_inv_1_mult_pow_diff_pos_new,
                                    results_bin_inv_1_mult_alpha_OR1_diff_pos_new,
                                    results_bin_inv_1_mult_pow_OR1_diff_pos_new) %>%
  mutate(scenario = factor(case_when(trend_param=="add" & lambda0 >=0 ~ "add_pos",
                                     trend_param=="add" & lambda0 <0 ~ "add_neg",
                                     trend_param=="mult" & lambda0 >=0 ~ "mult_pos",
                                     trend_param=="mult" & lambda0 <0 ~ "mult_neg"),
                           levels = c("add_neg", "add_pos", "mult_neg", "mult_pos")),
         alpha = ifelse(hypothesis %in% c("H0", "H0_1"), 0.025, NA))

results_bin_diff_inv_2_new <- rbind(results_bin_inv_2_mult_alpha_diff_neg_new,
                                    results_bin_inv_2_mult_pow_diff_neg_new,
                                    results_bin_inv_2_mult_alpha_OR1_diff_neg_new,
                                    results_bin_inv_2_mult_pow_OR1_diff_neg_new,
                                    results_bin_inv_2_mult_alpha_diff_pos_new,
                                    results_bin_inv_2_mult_pow_diff_pos_new,
                                    results_bin_inv_2_mult_alpha_OR1_diff_pos_new,
                                    results_bin_inv_2_mult_pow_OR1_diff_pos_new) %>%
  mutate(scenario = factor(case_when(trend_param=="add" & lambda0 >=0 ~ "add_pos",
                                     trend_param=="add" & lambda0 <0 ~ "add_neg",
                                     trend_param=="mult" & lambda0 >=0 ~ "mult_pos",
                                     trend_param=="mult" & lambda0 <0 ~ "mult_neg"),
                           levels = c("add_neg", "add_pos", "mult_neg", "mult_pos")),
         alpha = ifelse(hypothesis %in% c("H0", "H0_1"), 0.025, NA))

results_bin_diff_inv_3_new <- rbind(results_bin_inv_3_mult_alpha_diff_neg_new,
                                    results_bin_inv_3_mult_pow_diff_neg_new,
                                    results_bin_inv_3_mult_alpha_OR1_diff_neg_new,
                                    results_bin_inv_3_mult_pow_OR1_diff_neg_new,
                                    results_bin_inv_3_mult_alpha_diff_pos_new,
                                    results_bin_inv_3_mult_pow_diff_pos_new,
                                    results_bin_inv_3_mult_alpha_OR1_diff_pos_new,
                                    results_bin_inv_3_mult_pow_OR1_diff_pos_new) %>%
  mutate(scenario = factor(case_when(trend_param=="add" & lambda0 >=0 ~ "add_pos",
                                     trend_param=="add" & lambda0 <0 ~ "add_neg",
                                     trend_param=="mult" & lambda0 >=0 ~ "mult_pos",
                                     trend_param=="mult" & lambda0 <0 ~ "mult_neg"),
                           levels = c("add_neg", "add_pos", "mult_neg", "mult_pos")),
         alpha = ifelse(hypothesis %in% c("H0", "H0_1"), 0.025, NA))

results_bin_diff_new <- rbind(results_bin_diff_step_new %>% select(-c(p_0, p_1, p_2, p1, p_a2_OR, p_a2_RR, p_a2_RD)),
                              results_bin_diff_lin_new %>% select(-c(p_0, p_1, p_2, p1, p_a2_OR, p_a2_RR, p_a2_RD)),
                              results_bin_diff_inv_1_new %>% select(-N_peak),
                              results_bin_diff_inv_2_new %>% select(-N_peak),
                              results_bin_diff_inv_3_new %>% select(-N_peak))
```



## Bias (Fig. S14) - corrected

```{r, fig.width=10, fig.height=10}
hypothesis_names <- c(H0="Null hypothesis (OR1<1)", H1="Alter. hypothesis (OR1<1)", H0_1="Null hypothesis (OR1>1)", H1_1="Alter. hypothesis (OR1>1)")
trend_names <- c(linear = "Linear", stepwise = "Stepwise", inv_u_1 = "Inverted-U (N[p] == 125)", inv_u_2 = "Inverted-U (N[p] == 250)", inv_u_3 = "Inverted-U (N[p] == 500)")

ggplot(get_data_plot(results_bin_diff_new) %>% filter(model!="zsep" & model!="zpol", scenario=="mult_pos")) +
  #geom_point(aes(lambda1, bias, color=as.factor(model))) +
  geom_line(aes(lambda1, bias, color=as.factor(model)), size=1) +
  facet_grid(hypothesis ~ trend, scales = "free", 
             labeller = labeller(hypothesis  = as_labeller(hypothesis_names),
                                 trend = as_labeller(trend_names, label_parsed))) +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom") +
  labs(x=TeX("$\\lambda_1$"), color="Analysis approach:", y="Bias") +
  scale_color_manual(values = my_palette, labels = c("ALLTC-Linear", "ALLTCI-Linear", "ALLTC-Step", "ALLTCI-Step", "TC-Linear", "TC-Step", "Pooled approach", "Separate approach")) +
  scale_x_continuous(n.breaks = 3)

ggsave("figures/bin_all_diff_pos_bias_supp_new.png", width = 10, height = 10)
```

## rMSE (Fig. S15) - corrected

```{r, fig.width=10, fig.height=10}
hypothesis_names <- c(H0="Null hypothesis (OR1<1)", H1="Alter. hypothesis (OR1<1)", H0_1="Null hypothesis (OR1>1)", H1_1="Alter. hypothesis (OR1>1)")
trend_names <- c(linear = "Linear", stepwise = "Stepwise", inv_u_1 = "Inverted-U (N[p] == 125)", inv_u_2 = "Inverted-U (N[p] == 250)", inv_u_3 = "Inverted-U (N[p] == 500)")

ggplot(get_data_plot(results_bin_diff_new) %>% filter(model!="zsep" & model!="zpol", scenario=="mult_pos")) +
  #geom_point(aes(lambda1, rMSE, color=as.factor(model))) +
  geom_line(aes(lambda1, rMSE, color=as.factor(model)), size=1) +
  facet_grid(hypothesis ~ trend, scales = "free", 
             labeller = labeller(hypothesis  = as_labeller(hypothesis_names),
                                 trend = as_labeller(trend_names, label_parsed))) +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom") +
  labs(x=TeX("$\\lambda_1$"), color="Analysis approach:", y="rMSE") +
  scale_color_manual(values = my_palette, labels = c("ALLTC-Linear", "ALLTCI-Linear", "ALLTC-Step", "ALLTCI-Step", "TC-Linear", "TC-Step", "Pooled approach", "Separate approach")) +
  scale_x_continuous(n.breaks = 3)

ggsave("figures/bin_all_diff_pos_rmse_supp_new.png", width = 10, height = 10)
```




























